Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
Rest...
Figuras Libraries

@@

>>>>

\caption{Characterization of GUIDs groups} 
\label{tab:table5}
\begin{tabular}{c|ccc}\hline & \multicolumn{1}{c}{GUID Groups} & \multicolumn{2}{c}{Mean Value (99\% CI)} \\

\hline
\hline
\parbox[t]{2mm}{\multirow{6}{*}{\rotatebox[origin=c]{90}{eMule}}} & All & 4.3 (4.3, 4.4) & 4.1 (4.1, 4.1) \\
& TOR & 21.2 (19.9, 22.5) & 17.4 (16.9, 18.0)\\
& Relayed & 9.2 (8.9, 9.6) & 5.5 (5.4, 5.6)\\
& Multi-Network & 10.8 (10.6, 11.0) & 9.5 (9.4, 9.7)\\
& Top 10\% Obs. & 23.5 (23.2, 23.8) & 22.3 (22.2, 22.4)\\
& Top 10\% Corp. & 27.8 (27.4, 28.5) & 18.7 (18.6, 18.8)\\
& Top 10\% Contr. & 25.8 (25.4, 26.5) & 19.0 (18.9, 19.1)\\
\hline

@@

\item[\checkmark]The relationship between p2p network GUIDs and real users is not one-to-one in the dataset.

\item[\checkmark]A single user may correspond to multiple GUIDs.

\item[\checkmark]This is known as \textit{user aliasing}, and may be intentional.

\begin{block}{Reasons for deliberate aliasing can be:}

\item[\checkmark]A user has two computers (or multiple
accounts on a single computer), each with an installation
of Gnutella.

\item[\checkmark]A user may reinstall or upgrade their p2p client on a single computer or modify their GUID over time.

\item[\checkmark]
